Optimizing Abstract$^{\text 2}$ Machines

### 2012-11-01 paper/paper.tex

>>>>

\subsection{Another problem with acceptability: Temporal ignorance}

The small-step approach to static analysis brings subtle yet important temporal
richness not found in classical analyses for higher-order programs.
%
Classical analyses (ultimately) compute judgments on program terms and
contexts, e.g., at expression $e$, value $x$ may have value $v$.
%
The judgments do not relate the order in which expressions and context may be
evaluated in a program, e.g., a classical analysis has nothing to say with
regard to question like, ``Do we always evaluate $e_1$ before $e_2$?'' or ``Is
it always the case that a file handle is opened, read and then closed in that
order?''

Small-step analyses, by their nature, encode the temporal relationships between
abstract states.
%
It is sensible to make temporal queries of a small-step analysis.
%
Of course, this does not come for free: respecting temporal order imposes an
order in which states and terms may be evaluated \emph{during} the analysis.
%
Classical analyses can (and do) evaluate expressions in any order, or in some
cases, even in parallel~\cite{might:Prabhu:2010:EigenCFA}.
%
Relaxing that restriction on order affords additional optimizations that we
have \emph{not} performed.

We avoid sacrificing order not simply because we are interested in the
questions it allows us to ask, but because considering temporal order actually
improves the precision of the analysis itself.
